FinalManuscript_DISCS_UG

### 2019-04-29 parts/03_methodology.tex
Final revisions and cleanup

Four homomorphic encryption schemes were investigated. For cryptosystems with readily available open-source implementations, such implementations were used. For the remaining cryptosystems, the encryption and decryption methods were implemented in Python.
\begin{itemize}
	\item The Paillier cryptosystem is incorporated using the \texttt{python-paillier} library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
	\item The DGHV cryptosystem is ported from the C++ implementation at 
	\url{https://github.com/deevashwer/Fully-Homomorphic-DGHV-and-Variants}.
	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
\end{itemize}

For convenience, a wrapper library was created that integrates the four cryptosystems into a unified interface.

The Paillier and DGK cryptosystems were adapted for floating-point computations using the protocols described in section \ref{sec:fp_arithmetic}.

@@

\subsection{Facial Recognition Tests}
%% TODO: Brian, can you fill this part up? Yes. OK Thanks
The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} was implemented for this study.
%Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.
Training and test data were secured from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

>>>>

Four homomorphic encryption schemes were investigated. For cryptosystems with readily available open-source implementations, such implementations were used. For the remaining cryptosystems, the encryption and decryption methods were implemented in Python 3.7.1.
\begin{itemize}
	\item The Paillier cryptosystem is incorporated using the \texttt{python-paillier} library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
	\item The DGHV cryptosystem is ported from the C++ implementation at 
	\url{https://github.com/deevashwer/Fully-Homomorphic-DGHV-and-Variants}.
	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
\end{itemize}

A wrapper library was created that integrates the four cryptosystems into a unified interface.
The Paillier and DGK cryptosystems were adapted for floating-point computations using the protocols described in section \ref{sec:fp_arithmetic}.

@@

\subsection{Facial Recognition Tests}
The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} was implemented for this study.
%Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.
Training and test data were secured from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

### 2019-04-29 parts/03_methodology_02nonlinearintensitytransformations.tex
Final revisions and cleanup

\section{Non-Linear Intensity Transformations}
Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
We now describe how we implement the logarithm and power-law image intensity transformations. In the case of partially homomorphic cryptosystems (Paillier, DGK), if  exponentiation and multiplication is required, the secure protocols in section \ref{ssec:exponentiationprotocol} will be used.

@@

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{sec:logarithm_approximation}.
\begin{align*}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:optimal_log_approximation_ch3}.

>>>>

\section{Non-Linear Intensity Transformations}
Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}. We now describe how we implement the logarithm and power-law image intensity transformations.

@@

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{sec:power_approximation}.
\begin{align*}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:optimal_log_approximation_ch3}. For the implementation of the power-law transformation, a partial sum consisting of the first five terms of the infinite series were used.

### 2019-04-29 parts/04_results.tex
Add chapter 5
Final revisions and cleanup

\chapter{RESULTS AND DISCUSSION}
The results shown in this section are gathered from the tests for intensity transformations under Paillier and DGK cryptosystems. During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e. the results vary drastically every time the same tests were done). This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.

@@

\begin{table*}
	\centering
	\caption{Comparison of intensity transformations under Paillier}
	\label{tbl:it-pal}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.5cm}}}
		\hline
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm trans.} & \multicolumn{2}{c}{Power-law trans.} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
		\hline
		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
		(#2) & \includegraphics[width=1.5cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.5cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
		\hline
	\end{tabular}
\end{table*}

\begin{table*}
	\centering
	\caption{Comparison of intensity transformations under DGK}
	\label{tbl:it-dgk}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.5cm}}}
		\hline
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm trans.} & \multicolumn{2}{c}{Power-law trans.} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
		\hline
		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
		(#2) & \includegraphics[width=1.5cm]{out_faces/dgk_negate_#1_original.png} & \includegraphics[width=1.5cm]{out_faces/dgk_negate_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/dgk_negate_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/dgk_logtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/dgk_logtransform_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/dgk_pwrtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/dgk_pwrtransform_#1_decrypted.png} \\ }%
		\hline
	\end{tabular}
\end{table*}

@@

\subsection{Power-Law Transformation}
Applying the power-law transformation under both cryptosystems produced less than accurate images. The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}. As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.

@@

When DGK was used in the power-law transformation, it failed to produce a discernible image and only resulted in an almost black image with a faint shape of a face. The mean squared errors for this case is an order of magnitude higher than the results from using Paillier. Furthermore, doing a power-law transformation under DGK is not only impractical in terms of accuracy, but also it is somewhat impractical in terms of time efficiency because it took at most 4 minutes to process each image.

\begin{table}[t]
	\centering
	\caption{Power-law transformation under DGK}
	\label{tbl:pwr-dgk}
    \begin{tabular}{lcccccc}
        \hline
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
		(a) & 14777.466 & 6.435 & 0.12778 & 0.677 & 204.491 & 0.978 \\
		(b) & 13343.854 & 6.878 & 0.07894 & 0.913 & 232.692 & 0.663 \\
		(c) & 10885.568 & 7.762 & 0.09146 & 0.696 & 198.959 & 0.590 \\
		(d) & 7218.081 & 9.547 & 0.10182 & 0.658 & 160.924 & 0.461 \\
		(e) & 9994.237 & 8.133 & 0.09100 & 0.518 & 166.274 & 0.507 \\
		(f) & 19141.793 & 5.311 & 0.08388 & 0.531 & 193.571 & 0.606 \\
		(g) & 13213.915 & 6.920 & 0.09794 & 0.656 & 163.594 & 0.455 \\
		(h) & 7444.691 & 9.412 & 0.09291 & 0.522 & 160.426 & 0.463 \\
		(i) & 21349.488 & 4.837 & 0.17239 & 0.526 & 160.191 & 0.446 \\
		(j) & 13776.770 & 6.739 & 0.10769 & 0.489 & 156.763 & 0.460 \\
		\hline
    \end{tabular}
\end{table}

>>>>

\chapter{RESULTS AND DISCUSSION}
The results shown in this section are gathered from the tests for intensity transformations under Paillier and DGK cryptosystems. During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e. the results vary drastically every time the same tests were done). This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}. Results obtained from the DGHV cryptosystem were also unstable, but DGHV was also impractical, taking over 5 minutes to perform a single floating-point addition operation.

@@

\begin{table}
	\centering
	\caption{Comparison of intensity transformations under Paillier}
	\label{tbl:it-pal}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.5cm}}}
		\hline
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm trans.} & \multicolumn{2}{c}{Power-law trans.} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
		\hline
		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
		(#2) & \includegraphics[width=1.5cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.5cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
		\hline
	\end{tabular}
\end{table}

\begin{table}
	\centering
	\caption{Comparison of intensity transformations under DGK}
	\label{tbl:it-dgk}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.5cm}}}
		\hline
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm trans.} & \multicolumn{2}{c}{Power-law trans.} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
		\hline
		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
		(#2) & \includegraphics[width=1.5cm]{out_faces/dgk_negate_#1_original.png} & \includegraphics[width=1.5cm]{out_faces/dgk_negate_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/dgk_negate_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/dgk_logtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/dgk_logtransform_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/dgk_pwrtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/dgk_pwrtransform_#1_decrypted.png} \\ }%
		\hline
	\end{tabular}
\end{table}

@@

\subsection{Power-Law Transformation}
Applying the power-law transformation under both cryptosystems did not produce accurate images. The accuracy varies greatly across all the images. When Paillier was used, mean squared errors ranged from 616.419 to 8270.696, and SSIM scores ranged from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}. As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive, requiring repeated evaluation of the logarithm approximation.

@@

When DGK was used in the power-law transformation, it failed to produce a discernible image and only resulted in an almost black image with a faint shape of a face. The mean squared errors under DGK are an order of magnitude higher than the results from using Paillier. Furthermore, doing a power-law transformation under DGK is somewhat impractical in terms of time efficiency because it took at most 4 minutes to process each image.

\begin{table}[!ht]
	\centering
	\caption{Power-law transformation under DGK}
	\label{tbl:pwr-dgk}
    \begin{tabular}{lcccccc}
        \hline
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
		(a) & 14777.466 & 6.435 & 0.12778 & 0.677 & 204.491 & 0.978 \\
		(b) & 13343.854 & 6.878 & 0.07894 & 0.913 & 232.692 & 0.663 \\
		(c) & 10885.568 & 7.762 & 0.09146 & 0.696 & 198.959 & 0.590 \\
		(d) & 7218.081 & 9.547 & 0.10182 & 0.658 & 160.924 & 0.461 \\
		(e) & 9994.237 & 8.133 & 0.09100 & 0.518 & 166.274 & 0.507 \\
		(f) & 19141.793 & 5.311 & 0.08388 & 0.531 & 193.571 & 0.606 \\
		(g) & 13213.915 & 6.920 & 0.09794 & 0.656 & 163.594 & 0.455 \\
		(h) & 7444.691 & 9.412 & 0.09291 & 0.522 & 160.426 & 0.463 \\
		(i) & 21349.488 & 4.837 & 0.17239 & 0.526 & 160.191 & 0.446 \\
		(j) & 13776.770 & 6.739 & 0.10769 & 0.489 & 156.763 & 0.460 \\
		\hline
    \end{tabular}
\end{table}

### 2019-04-29 parts/05_conclusions.tex
Final revisions and cleanup

\section{Ongoing and Future Work}
Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available.
One of the authors of this paper has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.

Efforts are ongoing with regard to the facial recognition tests. Our own implementation of the privacy-preserving eigenfaces by Erkin, et al. does not yet use the DGK cryptosystem for secure integer comparison in the match finding step.

Another promising image operation to consider is \textit{facial detection} under a homomorphic cryptosystem. Work has been started in order to assess the feasibility of using Haar cascades in a privacy-preserving manner.

Future work would involve improving and optimizing our implementation of non-linear intensity transformations in terms of number of operations, numerical accuracy and stability, and time efficiency.
% Future work would involve improving and optimizing our implementation of the DGK cryptosystem so that it performs faster.
% A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
For future studies, an implementation of a client-server framework or system dealing with secure image processing can be considered.

>>>>

\section{Recommendations for Future Work}
Testing intensity transformations under the BGV cryptosystem may be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available.
One of the authors of this paper has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.

% Efforts are ongoing with regard to the facial recognition tests. Our own implementation of the privacy-preserving eigenfaces by Erkin, et al. does not yet use the DGK cryptosystem for secure integer comparison in the match finding step.

Another promising image operation to consider is \textit{facial detection} under a homomorphic cryptosystem. 
As secure floating-point operations and secure comparisons are feasible, it may be feasible to implement secure Haar cascades.
% Work has been started in order to assess the feasibility of using Haar cascades in a privacy-preserving manner.

Future studies would involve improving and optimizing our implementation of non-linear intensity transformations in terms of number of operations, numerical accuracy and stability, and time efficiency.
% Future work would involve improving and optimizing our implementation of the DGK cryptosystem so that it performs faster.
% A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
Furthermore, an implementation of a client-server framework or system dealing with secure image processing can be considered.
